Identifying Inter-Genomic Repeats Using Fast, Approximate Methods for Betweenness Centrality

### 2015-05-17 manuscript/manuscript.tex
benchmakrs added:

\usepackage{amssymb}
\usepackage{amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\newtheorem{mydef}{Definition}
\newtheorem{mylemma}{Lemma}
\usepackage{algorithm}
\usepackage{tabularx}
\usepackage[noend]{algpseudocode}

@@

>>>>

\usepackage{amssymb}
\usepackage{amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\newtheorem{mydef}{Definition}
\newtheorem{mylemma}{Lemma}
\usepackage{algorithm}
\usepackage{tabularx}

\usepackage[noend]{algpseudocode}

@@

\subsection*{Benchmarking Runtime of Sampling Algorithms}
We test how the runtime of both the algorithms change as we change size of the sample. We use the k-mer graph generated from the genome of \textit{Escherichia coli} str. K-12 with 311137 nodes and 279290 edges. For the algorithm based on node sampling, we tested runtime on the sample sizes 10, 100, 1000, 10000 and 50000. It is observed that runtime increases linearly with sample size(Figure \ref{fig:bm_nodes}). For the algorithm based on shortest path sampling, we varied the value of $\epsilon$ parameter which controls the sample size. Lesser the $\epsilon$ is, higher is the sample size. It is observed that as we increased epsilon, runtime decreased(Figure \ref{fig:bm_paths}).

\begin{figure}[ht]
\centering
\includegraphics[width=8cm,height=5cm]{benchmarknodes}
\caption{Plot of runtime against number of sampled nodes. It can be seen that there is a linear relation between these two.}
\label{fig:bm_nodes}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=8cm,height=5cm]{benchmarkpaths}
\caption{Plot of runtime against shortest path sample size. It can be seen that runtime increases with higher size sample.}
\label{fig:bm_paths}
\end{figure}
